### 2018-09-13 ICRA19/covControl.tex
tiny caption update
Added Haoran's images

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{angleOfReposeExp.pdf}
\end{center}
\caption{\label{fig:angleOfReposeExp}
Experimental data
}
\end{figure}

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{ironAndSaltCloseup.pdf}
\end{center}
\caption{\label{fig:ironAndSaltCloseup}
Magnified image of salt and iron at angle of repose.
}
\end{figure}

@@

\subsection{Hardware experiment: kilobot angle of repose}

In this section we vary the force and approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. 
 A Kilobot is a three-centimeter diameter,  low-cost robot with a light sensor. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp}. Figure \ref{fig:kilobotAngle} shows angle of repose of the Kilobots with three different angles of the pink rod when the rod has 0$^\circ$, 22.5$^\circ$ and 45$^\circ$. The green lines show the triangle that the robots pile up. The cyan star is the center of mass of the rod, and mean position and variance of the robots are shown with a red star and red ellipse.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\caption{\label{fig:SetUp}
The platform where we control Kilobots with lights.
}
\end{figure}

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{KilobotAngleThreeAngles.pdf}
\end{center}
\caption{\label{fig:kilobotAngle}
Angle of repose of Kilobots controlled by light.
}
\end{figure}

>>>>

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{aorPlot.pdf}
\end{center}
\caption{\label{fig:angleOfReposeExp}
Experimental data using iron particles and garvity.
}
\end{figure}

%\begin{figure}
%\begin{center}
%	\includegraphics[width=\columnwidth]{ironAndSaltCloseup.pdf}
%\end{center}
%\caption{\label{fig:ironAndSaltCloseup}
%Magnified image of salt and iron at angle of repose.
%}
%\end{figure}

@@

\subsection{Hardware experiment: kilobot angle of repose}
We varied the approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. 
 A Kilobot is a three-centimeter diameter,  low-cost robot. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp}, also showing angle of repose of the Kilobots with  the pink rod at three angles of attack: 90$^\circ$, 67.5$^\circ$ and 45$^\circ$. The green lines show the triangle shape the robots pile up into. The cyan star is the center of mass of the rod, and the mean position and variance of the robots are shown with  red stars and red ellipses.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\caption{\label{fig:SetUp}
Hardware platform for steering Kilobots with lights and characteristic shape formed by kilobot angle of repose for three angle of attacks.
}
\end{figure}
